The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
minor edits

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength was higher in foraging and open layers
compared to forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased when the social distance threshold increased from 5 m and 100 m in 
all three habitat layers followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allowed [e.g. from this study and @Peignier_2019;
@Lesmerises_2018] us to confirm the use of 50 m buffer that has long been used
for studies of ungulate social behaviour in the field [@Lingle_2003; @Clutton_1982].

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals in foraging layers
at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent in forest and open layers
as land cover resolution increased (Figure \@ref(fig:lcres) D). Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
with increasing spatial resolution, while decreasing in foraging habitat 
(`r count[res == 30 & lc == 3, percent]`% at 30 m
- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
indicated the importance of matching land cover resolution to scale of
habitat selection and choosing a land cover product with a resolution
sufficient to detect less common habitats.

>>>>

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength was higher in foraging and open layers
compared to forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased when the social distance threshold increased from 5 m and 100 m in 
all three habitat layers followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allowed  us to confirm the use of 50 m buffer 
[e.g. from this study and @Peignier_2019; @Lesmerises_2018] that has long been used
for studies of ungulate social behaviour in the field 
[@Lingle_2003; @Clutton_1982; @Kasozi_2020].

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals in foraging layers
at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent in forest and open layers
as land cover resolution increased (Figure \@ref(fig:lcres) D). Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
with increasing spatial resolution, while decreasing in foraging habitat 
(`r count[res == 30 & lc == 3, percent]`% at 30 m
- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
highlight the importance of matching land cover resolution to scale of
habitat selection and choosing a land cover product with a resolution
sufficient to detect less common habitats.
